---
title: "R Notebook"
output:
  html_notebook: default
  word_document:
    reference_docx: template.docx
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,eval = TRUE,warning = FALSE,message = FALSE)
```

# First steps
## Loading Librairies
```{r}
library(tidyverse)
library(ggrepel)
library(formattable)

customGreen0 = "#DeF7E9"
customGreen = "#71CA97"
customRed = "#ff7f7f"
customOrange = "#F58F28"
```

##Loading Devices data 
In that case the csv generated used the tabulation separator. Adapt the delim parameter to your specific use case (coma, semicolon etc).
```{r}
df <- read_delim(file = "./data-raw/DEX_Device_data_Blacstone_April2020.csv", delim = "\t")
df$`System boot duration baseline [s]` <- as.numeric(df$`System boot duration baseline [s]`)
df$`Logon duration baseline [s]` <- as.numeric(df$`Logon duration baseline [s]`)
df$`Number of cores` <- as.numeric(df$`Number of cores`)
head(df)
```

## Loading Application data
```{r}
df.app <- read_delim(file = "./data-raw/DEX_App_data_Blacstone_April2020.csv", delim = "\t")
df.app <- df.app %>%
  mutate(`Average memory usage per execution [MB]` = round(`Average memory usage per execution [bytes]`/(1024^2),2)) %>%
  select(everything(), -`Average memory usage per execution [bytes]`)
head(df.app)
```


## Loading Chrome Data
```{r}
df.chr <- read_delim(file = "./data-raw/DEX_Chrome_Blacstone_April2020.csv", delim = "\t")
df.chr <- df.chr %>%
  mutate(`Average memory usage per execution [MB]` = round(`Average memory usage per execution [bytes]`/(1024^2),1)) %>%
  select(everything(), -`Average memory usage per execution [bytes]`)
head(df.chr)
```

## Load Office Data
```{r}
df.office <- read_delim(file = "./data-raw/DEX_Office_Blacstone_April2020.csv", delim = "\t", col_types = cols(`Average memory usage per execution [bytes]` = col_number()) )
df.office <- df.office %>%
  mutate(`Average memory usage per execution [MB]` = round(`Average memory usage per execution [bytes]`/(1024^2),1)) %>%
  select(everything(), -`Average memory usage per execution [bytes]`, -`Application name`)
head(df.office)
```

# Devices
## DXS vs. OS Version and architecture
```{r fig.width=13,fig.height=8}
df %>%
  group_by(`OS version and architecture`) %>%
  summarize(`Number of devices` = n(),
   dex_score = mean(`Digital Experience Score (Digital Experience Score)`)) %>%
  mutate(`OS version and architecture` = str_replace_all(`OS version and architecture`,"Windows", "W")) %>%
  mutate(`OS version and architecture` = str_replace_all(`OS version and architecture`,"Enterprise", "E")) %>%
  mutate(`OS version and architecture` = str_replace_all(`OS version and architecture`,"Professional", "Pro")) %>%
  mutate(`OS version and architecture` = str_replace_all(`OS version and architecture`,"(64 bits)", "64")) %>%
  mutate(`OS version and architecture` = str_replace_all(`OS version and architecture`,"(32 bits)", "32")) %>%
  arrange(desc(`Number of devices`)) %>%
  ungroup() %>%
  ggplot(mapping = aes(x = reorder(`OS version and architecture`, -`Number of devices`))) +
  geom_bar(mapping = aes(y = `Number of devices`), stat = "identity", fill = "#1046A8", colour = "black") +
  geom_line(mapping = aes(y = dex_score * 300), colour = "#3194F7", group = 1) +
  geom_point(mapping = aes(y = dex_score * 300), colour = "#F9BA37", group = 1) +
  geom_text(mapping = aes(y = dex_score * 300, label = round(dex_score,1)), colour = "#FF7461", fontface="bold",group = 1, size = 5, vjust = -1) +
  scale_y_continuous(sec.axis = sec_axis(trans = ~ . /300, name = "DeX")) +
  theme_minimal() +
  labs(x = "") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 15),
        axis.text.y = element_text(size=12),
        axis.title = element_text(size=15))
ggsave("images/OS_dex_number_of_devices.png")
```


## DXS by Device Model
### All but Lenovo
```{r fig.width=17,fig.height=9}
df %>%
  filter(`Device manufacturer` != "Lenovo") %>%
  group_by(`Device model`) %>%
  summarize(number_of_devices = n(),
            DXS_Device = mean(`DXS - Device (DXS - Device)`, na.rm = T),
            DXS_Boot = mean(`Boot speed (DXS - Device)`, na.rm = T),
            DXS_Logon = mean(`Logon duration (DXS - Device)`, na.rm = T),
            DXS_BSOD = mean(`BSODs (DXS - Device)`, na.rm = T),
            DXS_Reset = mean(`Hard resets (DXS - Device)`, na.rm = T),
            DXS_Free_Space = mean(`System free space (DXS - Device)`, na.rm = T),
            DXS_CPU = mean(`CPU usage (DXS - Device)`, na.rm = T),
            DXS_Memory = mean(`Memory usage (DXS - Device)`, na.rm = T)
            ) %>%
  ungroup() %>%
  filter(number_of_devices >=25) %>%
  arrange(desc(number_of_devices)) %>%
  na.omit() %>%
  gather(key  = "DXS", value = "score", -`Device model`,-number_of_devices) %>%
  mutate(`DXS` = str_replace_all(`DXS`,"DXS_", "")) %>%
  ggplot(mapping = aes(x = reorder(`Device model`, -number_of_devices), y=score, fill = DXS)) +
  geom_bar(stat = "identity", position = "stack", alpha=0.8, color="black") +
  geom_text(aes(label=round(score,1), colour=score), position=position_stack(vjust = 0.5), size=6, show.legend = F) +
  geom_label(aes(y =-1, label=paste(number_of_devices, " devices")), show.legend = F, fill = "white", size=5)+
  scale_fill_manual(values = c("#111F65", "#3194F7", "#1046A8", "#F9BA37", "#BA74D2", "#08B3AB", "#FF7461", "#B3BBC8")) +
  scale_colour_continuous(low="red", high="black")+
  theme_void()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1,size = 14),
        legend.text = element_text(size = 14),
        legend.title = element_text(size=14))
ggsave("images/DXS_DeviceModel_number_of_devices.png")
```


### Lenovo
```{r fig.width=20,fig.height=15}
df %>%
  filter(`Device manufacturer` == "Lenovo") %>%
  group_by(`Device product version`) %>%
  summarize(number_of_devices = n(),
            DXS_Device = mean(`DXS - Device (DXS - Device)`, na.rm = T),
            DXS_Boot = mean(`Boot speed (DXS - Device)`, na.rm = T),
            DXS_Logon = mean(`Logon duration (DXS - Device)`, na.rm = T),
            DXS_BSOD = mean(`BSODs (DXS - Device)`, na.rm = T),
            DXS_Reset = mean(`Hard resets (DXS - Device)`, na.rm = T),
            DXS_Free_Space = mean(`System free space (DXS - Device)`, na.rm = T),
            DXS_CPU = mean(`CPU usage (DXS - Device)`, na.rm = T),
            DXS_Memory = mean(`Memory usage (DXS - Device)`, na.rm = T)
  ) %>%
  ungroup() %>%
  arrange(desc(number_of_devices)) %>%
  na.omit() %>%
  gather(key  = "DXS", value = "score", -`Device product version`,-number_of_devices) %>%
  mutate(`DXS` = str_replace_all(`DXS`,"DXS_", "")) %>%
  filter(score >0) %>%
  ggplot(mapping = aes(x = reorder(`Device product version`, -number_of_devices), y=score, fill = DXS)) +
  geom_bar(stat = "identity", position = "stack", alpha=0.8, color="black") +
  geom_text(aes(label=round(score,1), colour=score),position=position_stack(vjust = 0.5), size=5, show.legend = F) +
  geom_label(aes(y =-1, label=paste(number_of_devices, " devices")), show.legend = F, fill = "white", size=5)+
  scale_fill_manual(values = c("#111F65", "#3194F7", "#1046A8", "#F9BA37", "#BA74D2", "#08B3AB", "#FF7461", "#B3BBC8")) +
  scale_colour_continuous(low="red", high="black")+
  theme_void()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1,size = 16),
        legend.text = element_text(size = 14),
        legend.title = element_text(size=16))

ggsave("images/DXS_Lenovo_number_of_devices.png")
```

## CPU
```{r fig.width=22,fig.height=15}
df %>%
  group_by(`CPU model`) %>%
  summarize(number_of_devices = n(),
            `High CPU Time Ratio (mean)` = mean(`High device overall CPU time ratio [%]`, na.rm = T),
            `DXS CPU` = round(mean(`CPU usage (DXS - Device)`, na.rm = T),1),
            `DXS Device`= round(mean(`DXS - Device (DXS - Device)`, na.rm = T),1)
            ) %>%
  arrange(-number_of_devices) %>%
  filter(number_of_devices > 5) %>%
  #na.omit() %>%
  gather(key="DXS", value = "Score", -`CPU model`,-number_of_devices, -`High CPU Time Ratio (mean)`) %>%
  mutate(`DXS` = str_replace_all(`DXS`,"DXS ", ""),
         `CPU model` = str_replace(`CPU model`, " @ ", "\n")) %>%
  filter(number_of_devices >25) %>%
  ggplot(mapping = aes(x = `CPU model`))+
  geom_bar(mapping = aes(y=Score, fill = DXS), stat = "identity", position = "dodge", color="black", alpha=0.8)+
  geom_point(mapping = aes(y = `High CPU Time Ratio (mean)`*10), color="red", stat = "identity")+
  geom_label_repel(aes(y = `High CPU Time Ratio (mean)`*10, label= paste(round(`High CPU Time Ratio (mean)`,2),"%")),stat = "unique",size=6)+
  geom_label(aes(y =-1, label=paste(number_of_devices, " devices")), show.legend = F, fill = "white", size=6)+
  scale_y_continuous(sec.axis = sec_axis(~./10, name = "High CPU time ratio (%)")) +
  scale_fill_manual(values = c("#111F65", "#3194F7"))+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1,size = 16),
        axis.title = element_text(size = 16),
        axis.text = element_text(size = 16),
        legend.text = element_text(size = 16),
        legend.title = element_text(size=16))

ggsave("images/CPU_DEX_number_of_devices.png")

```

## Memory
```{r fig.width=17,fig.height=12}
df %>%
  mutate(`Total RAM [bytes]` = `Total RAM [bytes]`/(1024^3)) %>%
  mutate(`Total RAM [bytes]` = factor(`Total RAM [bytes]`)) %>%
  group_by(`Total RAM [bytes]`) %>%
  summarize(number_of_devices = n(),
            `High device memory time ratio [%]` = mean(`High device memory time ratio [%]`, na.rm = T),
            `DXS Memory` = round(mean(`Memory usage (DXS - Device)`, na.rm = T),1),
            `DXS Device`= round(mean(`DXS - Device (DXS - Device)`, na.rm = T),1)
            ) %>%
  arrange(-number_of_devices) %>%
  filter(number_of_devices > 5) %>%
  na.omit() %>%
  gather(key="DXS", value = "Score", -`Total RAM [bytes]`,-number_of_devices, -`High device memory time ratio [%]`) %>%
  mutate(`DXS` = str_replace_all(`DXS`,"DXS ", "")) %>%
  filter(number_of_devices > 10) %>%
  ggplot(mapping = aes(x = `Total RAM [bytes]`))+
  geom_bar(mapping = aes(y=Score, fill = DXS), stat = "identity", position = "dodge", color="black", alpha=0.8)+
  geom_point(mapping = aes(y = `High device memory time ratio [%]`/10), color="red", stat = "identity")+
  geom_line(mapping = aes(y = `High device memory time ratio [%]`/10), color="red", stat = "identity", group=1)+
  geom_label_repel(aes(y = `High device memory time ratio [%]`/10, label= paste(round(`High device memory time ratio [%]`,2),"%")),stat = "unique", size=5)+
  geom_label(aes(y =-0.2, label=paste(number_of_devices, " devices")), show.legend = F, fill = "white", size=5)+
  scale_y_continuous(sec.axis = sec_axis(~.*10, name = "High Memory time ratio")) +
  scale_fill_manual(values = c("#111F65", "#3194F7"))+
  theme_minimal()+
  labs(x="RAM")+
  theme(axis.text = element_text(size = 16),
        axis.title = element_text(size = 16),
        legend.text = element_text(size = 14),
        legend.title = element_text(size=14))
ggsave("images/Memory_DEX_number_of_devices.png")
```


## Boot
### General
```{r fig.width=17,fig.height=12}
df %>%
  group_by(boot_interval = cut_width(`System boot duration baseline [s]`, 10, boundary = 10)) %>%
  summarize(number_of_devices = n()) %>%
  na.omit() %>%
  filter(number_of_devices > 20) %>%
  ggplot(mapping = aes(x=boot_interval)) +
  geom_bar(aes(y=number_of_devices), stat = "identity", fill="#111F65", color="black") +
  geom_label(aes(y =number_of_devices, label=paste(number_of_devices, " devices")), show.legend = F, fill = "white", size=5)+
  theme_minimal() +
  labs(x="Boot time (s)", y="Number of devices")+
  theme(axis.text = element_text(size = 16),
        axis.title = element_text(size = 16))

```

### All Models (exluding Lenovo)
```{r echo=FALSE, eval=TRUE, fig.align="center", message=FALSE, fig.width=17,fig.height=12}
df %>%
  filter(`Device manufacturer` != "Lenovo") %>%
  group_by(`Device model`) %>%
  summarize(number_of_devices = n(),
            DXS_Device = mean(`DXS - Device (DXS - Device)`, na.rm = T),
            DXS_Boot = mean(`Boot speed (DXS - Device)`, na.rm = T),
            Boot_duration = mean(`System boot duration baseline [s]`, na.rm = T)
            ) %>%
  ungroup() %>%
  filter(number_of_devices >=25) %>%
  arrange(desc(number_of_devices)) %>%
  na.omit() %>%
  gather(key  = "DXS", value = "Score", -`Device model`,-number_of_devices,-Boot_duration) %>%
  mutate(`DXS` = str_replace_all(`DXS`,"DXS_", "")) %>%
  ggplot(mapping = aes(x = reorder(`Device model`, -number_of_devices)))+
  geom_bar(mapping = aes(y=Score, fill = DXS), stat = "identity", position = "dodge", color="black", alpha=0.8)+
  geom_point(mapping = aes(y = Boot_duration/10), color="red", stat = "identity")+
  geom_label_repel(aes(y = Boot_duration/10, label= paste(round(Boot_duration,1),"s")),stat = "unique", size=5)+
  geom_label(aes(y =-0.1, label=paste(number_of_devices, " devices")), show.legend = F, fill = "white", size=5)+
  scale_y_continuous(sec.axis = sec_axis(~.*10, name = "Boot duration (s)")) +
  scale_fill_manual(values = c("#111F65", "#3194F7"))+
  theme_minimal()+
  labs(x="")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1,size = 16),
        axis.text = element_text(size = 16),
        axis.title = element_text(size = 16),
        legend.text = element_text(size = 14),
        legend.title = element_text(size=14))
ggsave("images/DXS_All_noLenovo_boot.png")

```

### Lenovo only
```{r fig.width=17,fig.height=12}
df %>%
  filter(`Device manufacturer` == "Lenovo") %>%
  group_by(`Device product version`) %>%
  summarize(number_of_devices = n(),
            DXS_Device = mean(`DXS - Device (DXS - Device)`, na.rm = T),
            DXS_Boot = mean(`Boot speed (DXS - Device)`, na.rm = T),
            Boot_duration = mean(`System boot duration baseline [s]`, na.rm = T)
            ) %>%
  ungroup() %>%
  filter(number_of_devices >=5) %>%
  arrange(desc(number_of_devices)) %>%
  na.omit() %>%
  gather(key  = "DXS", value = "Score", -`Device product version`,-number_of_devices,-Boot_duration) %>%
  mutate(`DXS` = str_replace_all(`DXS`,"DXS_", "")) %>%
  ggplot(mapping = aes(x = reorder(`Device product version`, -number_of_devices)))+
  geom_bar(mapping = aes(y=Score, fill = DXS), stat = "identity", position = "dodge", color="black", alpha=0.8)+
  geom_point(mapping = aes(y = Boot_duration/10), color="red", stat = "identity")+
  geom_label_repel(aes(y = Boot_duration/10, label= paste(round(Boot_duration,1)," sec")),stat = "unique", size=5)+
  geom_label(aes(y =-0.2, label=paste(number_of_devices, " devices")), show.legend = F, fill = "white", size=5)+
  scale_y_continuous(sec.axis = sec_axis(~.*10, name = "Boot duration (s)")) +
  scale_fill_manual(values = c("#111F65", "#3194F7"))+
  labs(x="")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1,size = 16),
        axis.text = element_text(size = 16),
        axis.title = element_text(size = 16),
        legend.text = element_text(size = 14),
        legend.title = element_text(size=14))
ggsave("images/DXS_All_noLenovo_boot.png")

```

### OS
```{r fig.width=13,fig.height=8}
df %>%
  group_by(`OS version and architecture`) %>%
  summarize(`number_of_devices` = n(),
            DXS_Device = mean(`DXS - Device (DXS - Device)`, na.rm = T),
            DXS_Boot = mean(`Boot speed (DXS - Device)`, na.rm = T),
            Boot_duration = mean(`System boot duration baseline [s]`, na.rm = T)) %>%
  mutate(`OS version and architecture` = str_replace_all(`OS version and architecture`,"Windows", "W")) %>%
  mutate(`OS version and architecture` = str_replace_all(`OS version and architecture`,"Enterprise", "E")) %>%
  mutate(`OS version and architecture` = str_replace_all(`OS version and architecture`,"Professional", "Pro")) %>%
  mutate(`OS version and architecture` = str_replace_all(`OS version and architecture`,"(64 bits)", "64")) %>%
  mutate(`OS version and architecture` = str_replace_all(`OS version and architecture`,"(32 bits)", "32")) %>%
  arrange(desc(`number_of_devices`)) %>%
  ungroup() %>%
  filter(number_of_devices >=5) %>%
  arrange(desc(number_of_devices)) %>%
  na.omit() %>%
  gather(key  = "DXS", value = "Score", -`OS version and architecture`,-number_of_devices,-Boot_duration) %>%
  mutate(`DXS` = str_replace_all(`DXS`,"DXS_", "")) %>%
  ggplot(mapping = aes(x = reorder(`OS version and architecture`, -number_of_devices)))+
  geom_bar(mapping = aes(y=Score, fill = DXS), stat = "identity", position = "dodge", color="black", alpha=0.8)+
  geom_point(mapping = aes(y = Boot_duration/10), color="red", stat = "identity")+
  geom_label_repel(aes(y = Boot_duration/10, label= paste(round(Boot_duration,1)," sec")),stat = "unique", size=5)+
  geom_label(aes(y =-0.3, label=paste(number_of_devices, " devices")), show.legend = F, fill = "white",size=5)+
  scale_y_continuous(sec.axis = sec_axis(~.*10, name = "Boot duration (s)")) +
  scale_fill_manual(values = c("#111F65", "#3194F7"))+
  theme_minimal()+
  labs(x="")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1,size = 16),
        axis.text = element_text(size = 16),
        axis.title = element_text(size = 16),
        legend.text = element_text(size = 14),
        legend.title = element_text(size=14))
ggsave("images/DXS_OS_boot.png")
```

## Logon
```{r fig.width=17,fig.height=12}
df %>%
  group_by(logon_interval = cut_width(`Logon duration baseline [s]`, 10, boundary = 10)) %>%
  summarize(number_of_devices = n(),
            network_response = mean(`Average network response time [ms]`,na.rm = T)) %>%
  na.omit() %>%
  filter(number_of_devices > 20) %>%
  ggplot(mapping = aes(x=logon_interval)) +
  geom_bar(aes(y=number_of_devices), stat = "identity", fill="#111F65", color="black",alpha=0.9) +
  geom_label(aes(y =-1, label=paste(number_of_devices, " devices")), show.legend = F, fill = "white",size=5) +
  geom_point(aes(y=network_response*10))+
  geom_line(aes(y=network_response*10), group=1, color="#FF7461")+
  scale_y_continuous(sec.axis = sec_axis(~./10, name = "Network response time (ms)")) +
  theme_minimal()+
  labs(x="Logon time (s)", y="Number of devices")+
  theme(axis.text.x = element_text(size = 16),
        axis.text = element_text(size = 16),
        axis.title = element_text(size = 16),
        axis.title.y.right  = element_text(size = 16, colour = "red"),
        legend.text = element_text(size = 14),
        legend.title = element_text(size=14))
```

### AD Site
```{r fig.width=17,fig.height=12}
df %>%
  group_by(`AD site`) %>%
  summarize(number_of_devices = n(),
            DXS_Device = round(mean(`DXS - Device (DXS - Device)`, na.rm = T),1),
            DXS_logon = round(mean(`Logon duration (DXS - Device)`, na.rm = T),1),
            logon_response_time = round(mean(`Logon duration baseline [s]`, na.rm = T),1),
            network_response = round(mean(`Average network response time [ms]`, na.rm = T),1)) %>%
  ungroup() %>%
  na.omit() %>%
  gather(key  = "DXS", value = "Score", -network_response,-number_of_devices,-logon_response_time,-`AD site`) %>%
  mutate(`DXS` = str_replace_all(`DXS`,"DXS_", "")) %>%
  filter(number_of_devices > 25) %>%
  ggplot(mapping = aes(x = `AD site`)) +
  geom_col(aes(y = network_response), width = .4, fill = "#111F65", position = position_nudge(-.2), colour = "Black") +
  geom_col(aes(y = logon_response_time*5), fill = "#3194F7", width = .4, position = position_nudge(.2), colour = "Black")+
  geom_label(aes(y =-1, label=paste(number_of_devices, " devices")), show.legend = F, fill = "white", size=5) +
  scale_y_continuous(sec.axis = sec_axis(~./5, name="Logon time (s)"))+
  labs(y = "Network Response Time (ms)", fill = "OS") +
  theme_minimal()+
   theme(axis.text.x = element_text(size = 16),
         axis.title.y.left = element_text(size = 16, colour = "#111F65"),
         axis.title.y.right  = element_text(size = 16, colour = "#3194F7"),
         axis.text = element_text(size = 16),
         axis.title = element_text(size = 16),
         legend.text = element_text(size = 14),
         legend.title = element_text(size=14))

```


### Devices (no Lenovo)
```{r fig.width=20,fig.height=14}
df %>%
  filter(`Device manufacturer` != "Lenovo") %>%
  group_by(`Device model`) %>%
  summarize(number_of_devices = n(),
            DXS_Device = round(mean(`DXS - Device (DXS - Device)`, na.rm = T),1),
            DXS_logon = round(mean(`Logon duration (DXS - Device)`, na.rm = T),1),
            logon_response_time = round(mean(`Logon duration baseline [s]`, na.rm = T),1),
            network_response = round(mean(`Average network response time [ms]`, na.rm = T),1)) %>%
  ungroup() %>%
  filter(number_of_devices >=25) %>%
  arrange(desc(number_of_devices)) %>%
  na.omit() %>%
  gather(key  = "DXS", value = "Score", -network_response,-number_of_devices,-logon_response_time,-`Device model`) %>%
  mutate(`DXS` = str_replace_all(`DXS`,"DXS_", "")) %>%
  filter(number_of_devices > 25) %>%
  ggplot(mapping = aes(x = `Device model`)) +
  geom_col(aes(y = network_response), width = .4, fill = "#111F65", position = position_nudge(-.2), colour = "Black") +
  geom_col(aes(y = logon_response_time*5), fill = "#3194F7", width = .4, position = position_nudge(.2), colour = "Black")+
  geom_label(aes(y =-1, label=paste(number_of_devices, " devices")), show.legend = F, fill = "white", size=5) +
  scale_y_continuous(sec.axis = sec_axis(~./5, name="Logon time (s)"))+
  labs(y = "Network Response Time (ms)", fill = "OS") +
  theme_minimal()+
  theme(axis.text.x = element_text(size = 16, angle = 45, hjust = 1),
        axis.title.y.left = element_text(size = 16, colour = "#111F65"),
        axis.title.y.right  = element_text(size = 16, colour = "#3194F7"),
        axis.text = element_text(size = 16),
        axis.title = element_text(size = 16),
        legend.text = element_text(size = 14),
        legend.title = element_text(size=14))
```


### Devices (only Lenovo)
```{r fig.width=17,fig.height=12}
df %>%
  filter(`Device manufacturer` == "Lenovo") %>%
  group_by(`Device product version`) %>%
  summarize(number_of_devices = n(),
            DXS_Device = round(mean(`DXS - Device (DXS - Device)`, na.rm = T),1),
            DXS_logon = round(mean(`Logon duration (DXS - Device)`, na.rm = T),1),
            logon_response_time = round(mean(`Logon duration baseline [s]`, na.rm = T),1),
            network_response = round(mean(`Average network response time [ms]`, na.rm = T),1)) %>%
  ungroup() %>%
  arrange(desc(number_of_devices)) %>%
  na.omit() %>%
  gather(key  = "DXS", value = "Score", -network_response,-number_of_devices,-logon_response_time,-`Device product version`) %>%
  mutate(`DXS` = str_replace_all(`DXS`,"DXS_", "")) %>%
  filter(number_of_devices >= 5) %>%
  ggplot(mapping = aes(x = `Device product version`)) +
  geom_col(aes(y = network_response), width = .4, fill = "#111F65", position = position_nudge(-.2), colour = "Black") +
  geom_col(aes(y = logon_response_time*5), fill = "#3194F7", width = .4, position = position_nudge(.2), colour = "Black")+
  geom_label(aes(y =-1, label=paste(number_of_devices, " devices")), show.legend = F, fill = "white",size=5) +
  scale_y_continuous(sec.axis = sec_axis(~./5, name="Logon time (s)"))+
  labs(y = "Network Response Time (ms)", fill = "OS") +
  theme_minimal()+
  theme(axis.text.x = element_text(size = 16, angle = 45, hjust = 1),
        axis.title.y.left = element_text(size = 16, colour = "#111F65"),
        axis.title.y.right  = element_text(size = 16, colour = "#3194F7"),
        axis.text = element_text(size = 16),
        axis.title = element_text(size = 16),
        legend.text = element_text(size = 14),
        legend.title = element_text(size=14))
```

```{r fig.width=17,fig.height=12}
df %>%
  group_by(`OS version and architecture`) %>%
  summarize(`number_of_devices` = n(),
            DXS_Device = round(mean(`DXS - Device (DXS - Device)`, na.rm = T),1),
            DXS_logon = round(mean(`Logon duration (DXS - Device)`, na.rm = T),1),
            logon_response_time = round(mean(`Logon duration baseline [s]`, na.rm = T),1),
            network_response = round(mean(`Average network response time [ms]`, na.rm = T),1)) %>%
  mutate(`OS version and architecture` = str_replace_all(`OS version and architecture`,"Windows", "W")) %>%
  mutate(`OS version and architecture` = str_replace_all(`OS version and architecture`,"Enterprise", "E")) %>%
  mutate(`OS version and architecture` = str_replace_all(`OS version and architecture`,"Professional", "Pro")) %>%
  mutate(`OS version and architecture` = str_replace_all(`OS version and architecture`,"(64 bits)", "64")) %>%
  mutate(`OS version and architecture` = str_replace_all(`OS version and architecture`,"(32 bits)", "32")) %>%
  arrange(desc(`number_of_devices`)) %>%
  ungroup() %>%
  filter(number_of_devices >=5) %>%
  arrange(desc(number_of_devices)) %>%
  na.omit() %>%
  gather(key  = "DXS", value = "Score", -network_response,-number_of_devices,-logon_response_time,-`OS version and architecture`) %>%
  mutate(`DXS` = str_replace_all(`DXS`,"DXS_", "")) %>%
  filter(number_of_devices >= 5) %>%
  ggplot(mapping = aes(x = `OS version and architecture`)) +
  geom_col(aes(y = network_response), width = .4, fill = "#111F65", position = position_nudge(-.2), colour = "Black") +
  geom_col(aes(y = logon_response_time*5), fill = "#3194F7", width = .4, position = position_nudge(.2), colour = "Black")+
  geom_label(aes(y =-1, label=paste(number_of_devices, " devices")), show.legend = F, fill = "white", size=5) +
  scale_y_continuous(sec.axis = sec_axis(~./5, name="Logon time (s)"))+
  labs(y = "Network Response Time (ms)", fill = "OS") +
  theme_minimal()+
  theme(axis.text.x = element_text(size = 16, angle = 45, hjust = 1),
        axis.title.y.left = element_text(size = 16, colour = "#111F65"),
        axis.title.y.right  = element_text(size = 16, colour = "#3194F7"),
        axis.text = element_text(size = 16),
        axis.title = element_text(size = 16),
        legend.text = element_text(size = 14),
        legend.title = element_text(size=14))
```


### RAM
```{r fig.width=17,fig.height=12}
df %>%
  group_by(ram = cut_width(`Total RAM [bytes]`/(1024^3), 10, boundary = 10)) %>%
  summarize(number_of_devices = n(),
            DXS_Device = round(mean(`DXS - Device (DXS - Device)`, na.rm = T),1),
            DXS_logon = round(mean(`Logon duration (DXS - Device)`, na.rm = T),1),
            logon_time = round(mean(`Logon duration baseline [s]`, na.rm = T),1),
            network_response = round(mean(`Average network response time [ms]`, na.rm = T),1)) %>%
  na.omit() %>%
  arrange(desc(number_of_devices)) %>%
  na.omit() %>%
  gather(key  = "DXS", value = "Score", -network_response,-number_of_devices,-logon_time,-ram) %>%
  mutate(`DXS` = str_replace_all(`DXS`,"DXS_", "")) %>%
  filter(number_of_devices > 5) %>%
  ggplot(mapping = aes(x = ram)) +
  geom_col(aes(y = network_response), width = .4, fill = "#111F65", position = position_nudge(-.2), colour = "Black") +
  geom_col(aes(y = logon_time*5), fill = "#3194F7", width = .4, position = position_nudge(.2), colour = "Black")+
  geom_label(aes(y =-1, label=paste(number_of_devices, " devices")), show.legend = F, fill = "white",size=5) +
  scale_y_continuous(sec.axis = sec_axis(~./5, name="Logon time (s)"))+
  labs(y = "Network Response Time (ms)", x="RAM") +
  theme_minimal()+
  theme(axis.text.x = element_text(size = 16),
        axis.title.y.left = element_text(size = 16, colour = "#111F65"),
        axis.title.y.right  = element_text(size = 16, colour = "#3194F7"),
        axis.text = element_text(size = 16),
        axis.title = element_text(size = 16),
        legend.text = element_text(size = 14),
        legend.title = element_text(size=14))
```

## BSOD and Hard Resets
### Hard Resets
```{r echo=FALSE, eval=TRUE, fig.align="center", warning=FALSE,message=FALSE, fig.width=17,fig.height=12}
df %>%
  group_by(`Number of hard resets`) %>%
  summarize(`Number of devices` = n()) %>%
  formattable(
              align=c("l","l"))
```

### Crahses
```{r echo=FALSE, eval=TRUE, fig.align="center", warning=FALSE,message=FALSE, fig.width=17,fig.height=12}
df %>%
  group_by(`Number of system crashes`) %>%
  summarize(`Number of devices` = n()) %>%
  formattable(
              align=c("l","l"))
```

### Hard resets vs RAM
```{r echo=FALSE, eval=TRUE, fig.align="center", warning=FALSE,message=FALSE, fig.width=17,fig.height=12}
ram_interval <- c("0-4","4-8","8-12","12-16","16-20","28-32")
df %>%
  group_by(`RAM (GB)` = cut_width(`Total RAM [bytes]`/(1024^3), 4, boundary = 4)) %>%
  summarize(`Number of devices` = n(),
            `Average Number of hard resets` = mean(`Number of hard resets`),
            `Average number of app crashes` = round(mean(`Number of application crashes`),0),
            `Average number of app freezes` = round(mean(`Number of application not responding events`),0)) %>%
  filter(`Number of devices` > 20) %>%
  mutate(`RAM (GB)` = ram_interval) %>%
  formattable(align = c("c","c","c","c","c"))

```

### Crashes vs RAM
```{r echo=FALSE, eval=TRUE, fig.align="center", warning=FALSE,message=FALSE, fig.width=17,fig.height=12}
ram_interval <- c("0-4","4-8","8-12","12-16","16-20","28-32")
df %>%
  group_by(`RAM (GB)` = cut_width(`Total RAM [bytes]`/(1024^3), 4, boundary = 4)) %>%
  summarize(`Number of devices` = n(),
            `Average Number of system crashes` = mean(`Number of system crashes`),
            `Average number of app crashes` = round(mean(`Number of application crashes`),0),
            `Average number of app freezes` = round(mean(`Number of application not responding events`),0)) %>%
  filter(`Number of devices` > 20) %>%
  mutate(`RAM (GB)` = ram_interval) %>%
  formattable(align = c("c","c","c","c","c"))


```

## Disk Space
```{r echo=FALSE, eval=TRUE, fig.align="center", warning=FALSE,message=FALSE, fig.width=17,fig.height=12}
df %>%
  group_by(disk_space_interval = cut_width(`System drive free space [bytes]`/(1024^3), 20, boundary = 0)) %>%
  summarize(number_of_devices = n()) %>%
  filter(number_of_devices >=25)%>%
  ggplot(mapping = aes(x=disk_space_interval)) +
  geom_bar(aes(y=number_of_devices), stat = "identity", fill="#111F65", color = "black")+
  labs(x="Disk space (GB)", y="Number of devices")+
  theme_minimal()+
  theme(axis.text.x = element_text(size = 16, angle = 45, hjust = 1),
        axis.text = element_text(size = 16),
        axis.title = element_text(size = 16),
        legend.text = element_text(size = 14),
        legend.title = element_text(size=14))
```


## Memory
```{r echo=FALSE, eval=TRUE, fig.align="center", warning=FALSE,message=FALSE, fig.width=17,fig.height=12}
df %>%
  group_by(high_memory_ratio = cut_width(`High device memory time ratio [%]`, 10, boundary = 0)) %>%
  summarize(number_of_devices = n(),
            memory=round(mean(`Total RAM [bytes]`/(1024^3)),0)) %>%
  filter(number_of_devices >=20) %>%
  ggplot(mapping = aes(x=high_memory_ratio)) +
  geom_bar(aes(y=number_of_devices), stat = "identity",fill="#111F65", color = "black")+
  geom_line(aes(y=memory*100), group=1)+
  geom_point(aes(y=memory*100))+
  geom_label_repel(aes(y=memory*100, label= paste(memory, " GB")),stat = "unique", size=5)+
  scale_y_continuous(sec.axis = sec_axis(~./100, name="RAM (GB)"))+
  labs(x="High Memory time ratio", y="Number of devices")+
  theme_minimal()+
  theme(axis.text.x = element_text(size = 16),
        axis.text = element_text(size = 16),
        axis.title = element_text(size = 16),
        legend.text = element_text(size = 14),
        legend.title = element_text(size=14))

```

## CPU
```{r echo=FALSE, eval=TRUE, fig.align="center", warning=FALSE,message=FALSE, fig.width=17,fig.height=12}
df %>%
  group_by(high_cpu_ratio = cut_width(`High device overall CPU time ratio [%]`, 10, boundary = 0)) %>%
  summarize(number_of_devices = n(),
            number_of_cores= round(mean(`Number of cores`,na.rm = T),0)) %>%
  #filter(number_of_devices >=20) %>%
  ggplot(mapping = aes(x=high_cpu_ratio)) +
  geom_bar(aes(y=number_of_devices), stat = "identity",fill="#111F65", color = "black")+
  geom_line(aes(y=number_of_cores*100), group=1)+
  geom_point(aes(y=number_of_cores*100))+
  scale_y_continuous(sec.axis = sec_axis(~./100, name="Cores"))+
  geom_label_repel(aes(y=number_of_cores*100, label= paste("#",number_of_cores)),stat = "unique",size=5)+
  theme_minimal()+
  labs(x="High cpu time ratio",y="Number of devices")+
  theme(axis.text.x = element_text(size = 16),
        axis.text = element_text(size = 16),
        axis.title = element_text(size = 16),
        legend.text = element_text(size = 14),
        legend.title = element_text(size=14))

```

# Applications
## Overview
```{r echo=FALSE, eval=TRUE, fig.align="center", warning=FALSE,message=FALSE, fig.width=17,fig.height=12}
df.app %>%
  group_by( `Application name`) %>%
  summarize(`Number of devices` = sum(`Number of devices`),
            `Number of executions` = sum(`Number of executions`),
            `Average memory usage per execution (MB)` = round(mean(`Average memory usage per execution [MB]`, na.rm = T),1)) %>%
  filter(`Number of devices`>100,`Average memory usage per execution (MB)` > 150) %>%
  arrange(-`Average memory usage per execution (MB)`) %>%
  formattable(align = c("c","c","c","c"))
```

## High number of Excecutions
```{r echo=FALSE, eval=TRUE, fig.align="center", warning=FALSE,message=FALSE, fig.width=17,fig.height=12}
df.app %>%
  group_by( `Application name`) %>%
  summarize(`Number of executions` = sum(`Number of executions`),
            `Average memory usage per execution (MB)` = round(mean(`Average memory usage per execution [MB]`, na.rm = T),1)) %>%
  filter(`Average memory usage per execution (MB)` > 40, `Number of executions` > 50000) %>%
  arrange(-`Number of executions`) %>%
  formattable(align = c("c","c","c"))
```

## Chrome
```{r echo=FALSE, eval=TRUE, fig.align="center", warning=FALSE,message=FALSE, fig.width=17,fig.height=12}
df.chr %>%
  select(everything(), -`Executable name`,-`Application name`) %>%
  arrange(-`Number of executions`) %>%
  filter(`Number of devices` >= 10 & `Number of executions` > 4000) %>%
  formattable(align=c("c","c","c","c"))
```

## Office
```{r echo=FALSE, eval=TRUE, fig.align="center", warning=FALSE,message=FALSE, fig.width=17,fig.height=12}
df.office %>%
  arrange(-`Average memory usage per execution [MB]`) %>%
  filter(`Number of devices` >= 500 & `Number of executions` > 4000) %>%
  formattable(align=c("c","c","c","c","c"))
```

### Excel
```{r echo=FALSE, eval=TRUE, fig.align="center", warning=FALSE,message=FALSE, fig.width=17,fig.height=12}
df.office %>%
  arrange(-`Average memory usage per execution [MB]`) %>%
  filter(`Executable name` == 'excel.exe') %>%
  filter(`Number of devices` >= 10 & `Number of executions` > 1000) %>%
  formattable(align=c("c","c","c","c"))
```


### Word
```{r echo=FALSE, eval=TRUE, fig.align="center", warning=FALSE,message=FALSE, fig.width=17,fig.height=12}
df.office %>%
  arrange(-`Average memory usage per execution [MB]`) %>%
  filter(`Executable name` == 'winword.exe') %>%
  filter(`Number of devices` >= 10 & `Number of executions` > 1000) %>%
  formattable(align=c("c","c","c","c"))
```


### PowerPoint
```{r echo=FALSE, eval=TRUE, fig.align="center", warning=FALSE,message=FALSE, fig.width=17,fig.height=12}
df.office %>%
  arrange(-`Average memory usage per execution [MB]`) %>%
  filter(`Executable name` == 'powerpnt.exe') %>%
  filter(`Number of devices` >= 10 & `Number of executions` > 1000) %>%
  formattable(align=c("c","c","c","c","c"))
```
